\noindent\textbf{Machine Learning-Based Configuration Recommendation for the
Variational Quantum Eigensolver: A Pilot Study.}

The Variational Quantum Eigensolver (VQE) depends on algorithmic choices such
as the parameterized circuit, classical optimizer, and circuit depth. Exhaustive
evaluation of these configurations becomes costly as molecular geometries and
candidate configurations increase. This paper investigates supervised learning
as a meta-recommender that ranks VQE configurations before their execution. We
analyze 486 noiseless statevector simulations for H$_2$, LiH, and BeH$_2$,
covering 27 molecular geometries and 18 configurations per geometry. FCI/CASCI
energies define the absolute-error labels, while only descriptors available
before VQE execution are used as model inputs. Dummy regression, Ridge, Random
Forest, and a multilayer perceptron (MLP) are evaluated through nested
cross-validation grouped by molecular geometry. Random Forest achieved the
lowest mean absolute error, whereas the MLP provided the best top-$k$
recommendations. Its top-3 set contained the best available configuration for
all geometries and reached the maximum attainable chemical-accuracy coverage
of 85.2\%, while avoiding 83.3\% of the exhaustive grid evaluations. A
leave-one-molecule-out experiment showed substantially weaker predictive
generalization. The results support configuration recommendation as a promising
use of machine learning for VQE, while also exposing the limitations of the
small, noiseless dataset.
